---
title: "Research Fairness and Research Intergrity: A cross-sectional surevy"
author: "Dr Joseph B Sempa"
date: "`r Sys.Date()`"
output:
  word_document:
    fig_caption: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    toc: yes
  html_document:
    fig_caption: yes
    toc: yes
  html_notebook:
    toc: yes
always_allow_html: true
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(results = 'asis')
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(tinytex)
library(gmodels)
library(readxl)
library(gtsummary)
library(caret)
library(leaps)
library(MASS)
library(predtools)
library(randomForest)
library(mice)
library(psfmi)
library(survey)
```


```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
# library(readr)
final_dataset <- read_csv("final_dataset.csv")[-c(19,27,45,122),] %>%
  mutate(`Which of the following best describes you?` = as.factor(ifelse(`Which of the following best describes you?`=='Other (please specify)', 'Researcher from the Global North',  `Which of the following best describes you?`)))
# pilotstudy_dataset <-
#   survey::svydesign(
#     id = ~`Respondent ID`,
#     # weights = ~pw, # target proportion/ actual sample proportion
#     data = dataset#,
#     # fpc = ~fpc # ((Population size-sample size)/(population size-1))^(1/2)
#   )
# negative questions for responsible research practices: 1,3,4,5,7,8,10,11,15,18,19
# negative questions for fair research practices: 1,2,10,12,13
final_dataset <- final_dataset %>%
  mutate(
    rpq1 = case_when(
      `responsible research Practices_q1` == 'Never' ~ 7,
      `responsible research Practices_q1` == 'Very Rarely' ~ 6,
      `responsible research Practices_q1` == 'Rarely' ~ 5,
      `responsible research Practices_q1` == 'Occasionally' ~ 4,
      `responsible research Practices_q1` == 'Frequently' ~ 3,
      `responsible research Practices_q1` == 'Very Frequently' ~ 2,
      `responsible research Practices_q1` == 'Always' ~ 1
    ),
    rpq2 = case_when(
      `responsible research Practices_q2` == 'Never' ~ 1,
      `responsible research Practices_q2` == 'Very Rarely' ~ 2,
      `responsible research Practices_q2` == 'Rarely' ~ 3,
      `responsible research Practices_q2` == 'Occasionally' ~ 4,
      `responsible research Practices_q2` == 'Frequently' ~ 5,
      `responsible research Practices_q2` == 'Very Frequently' ~ 6,
      `responsible research Practices_q2` == 'Always' ~ 7
    ),
    rpq3 = case_when(
      `responsible research Practices_q3` == 'Never' ~ 7,
      `responsible research Practices_q3` == 'Very Rarely' ~ 6,
      `responsible research Practices_q3` == 'Rarely' ~ 5,
      `responsible research Practices_q3` == 'Occasionally' ~ 4,
      `responsible research Practices_q3` == 'Frequently' ~ 3,
      `responsible research Practices_q3` == 'Very Frequently' ~ 2,
      `responsible research Practices_q3` == 'Always' ~ 1
    ),
    rpq4 = case_when(
      `responsible research Practices_q4` == 'Never' ~ 7,
      `responsible research Practices_q4` == 'Very Rarely' ~ 6,
      `responsible research Practices_q4` == 'Rarely' ~ 5,
      `responsible research Practices_q4` == 'Occasionally' ~ 4,
      `responsible research Practices_q4` == 'Frequently' ~ 3,
      `responsible research Practices_q4` == 'Very Frequently' ~ 2,
      `responsible research Practices_q4` == 'Always' ~ 1
    ),
    rpq5 = case_when(
      `responsible research Practices_q5` == 'Never' ~ 7,
      `responsible research Practices_q5` == 'Very Rarely' ~ 6,
      `responsible research Practices_q5` == 'Rarely' ~ 5,
      `responsible research Practices_q5` == 'Occasionally' ~ 4,
      `responsible research Practices_q5` == 'Frequently' ~ 3,
      `responsible research Practices_q5` == 'Very Frequently' ~ 2,
      `responsible research Practices_q5` == 'Always' ~ 1
    ),
    rpq6 = case_when(
      `responsible research Practices_q6` == 'Never' ~ 1,
      `responsible research Practices_q6` == 'Very Rarely' ~ 2,
      `responsible research Practices_q6` == 'Rarely' ~ 3,
      `responsible research Practices_q6` == 'Occasionally' ~ 4,
      `responsible research Practices_q6` == 'Frequently' ~ 5,
      `responsible research Practices_q6` == 'Very Frequently' ~ 6,
      `responsible research Practices_q6` == 'Always' ~ 7
    ),
    rpq7 = case_when(
      `responsible research Practices_q7` == 'Never' ~ 7,
      `responsible research Practices_q7` == 'Very Rarely' ~ 6,
      `responsible research Practices_q7` == 'Rarely' ~ 5,
      `responsible research Practices_q7` == 'Occasionally' ~ 4,
      `responsible research Practices_q7` == 'Frequently' ~ 3,
      `responsible research Practices_q7` == 'Very Frequently' ~ 2,
      `responsible research Practices_q7` == 'Always' ~ 1
    ),
    rpq8 = case_when(
      `responsible research Practices_q8` == 'Never' ~ 7,
      `responsible research Practices_q8` == 'Very Rarely' ~ 6,
      `responsible research Practices_q8` == 'Rarely' ~ 5,
      `responsible research Practices_q8` == 'Occasionally' ~ 4,
      `responsible research Practices_q8` == 'Frequently' ~ 3,
      `responsible research Practices_q8` == 'Very Frequently' ~ 2,
      `responsible research Practices_q8` == 'Always' ~ 1
    ),
    rpq9 = case_when(
      `responsible research Practices_q9` == 'Never' ~ 1,
      `responsible research Practices_q9` == 'Very Rarely' ~ 2,
      `responsible research Practices_q9` == 'Rarely' ~ 3,
      `responsible research Practices_q9` == 'Occasionally' ~ 4,
      `responsible research Practices_q9` == 'Frequently' ~ 5,
      `responsible research Practices_q9` == 'Very Frequently' ~ 6,
      `responsible research Practices_q9` == 'Always' ~ 7
    ),
    rpq10 = case_when(
      `responsible research Practices_q10` == 'Never' ~ 7,
      `responsible research Practices_q10` == 'Very Rarely' ~ 6,
      `responsible research Practices_q10` == 'Rarely' ~ 5,
      `responsible research Practices_q10` == 'Occasionally' ~ 4,
      `responsible research Practices_q10` == 'Frequently' ~ 3,
      `responsible research Practices_q10` == 'Very Frequently' ~ 2,
      `responsible research Practices_q10` == 'Always' ~ 1
    ),
    rpq11 = case_when(
      `responsible research Practices_q11` == 'Never' ~ 7,
      `responsible research Practices_q11` == 'Very Rarely' ~ 6,
      `responsible research Practices_q11` == 'Rarely' ~ 5,
      `responsible research Practices_q11` == 'Occasionally' ~ 4,
      `responsible research Practices_q11` == 'Frequently' ~ 3,
      `responsible research Practices_q11` == 'Very Frequently' ~ 2,
      `responsible research Practices_q11` == 'Always' ~ 1
    ),
    rpq12 = case_when(
      `responsible research Practices_q12` == 'Never' ~ 1,
      `responsible research Practices_q12` == 'Very Rarely' ~ 2,
      `responsible research Practices_q12` == 'Rarely' ~ 3,
      `responsible research Practices_q12` == 'Occasionally' ~ 4,
      `responsible research Practices_q12` == 'Frequently' ~ 5,
      `responsible research Practices_q12` == 'Very Frequently' ~ 6,
      `responsible research Practices_q12` == 'Always' ~ 7
    ),
    rpq13 = case_when(
      `responsible research Practices_q13` == 'Never' ~ 1,
      `responsible research Practices_q13` == 'Very Rarely' ~ 2,
      `responsible research Practices_q13` == 'Rarely' ~ 3,
      `responsible research Practices_q13` == 'Occasionally' ~ 4,
      `responsible research Practices_q13` == 'Frequently' ~ 5,
      `responsible research Practices_q13` == 'Very Frequently' ~ 6,
      `responsible research Practices_q13` == 'Always' ~ 7
    ),
    rpq14 = case_when(
      `responsible research Practices_q14` == 'Never' ~ 1,
      `responsible research Practices_q14` == 'Very Rarely' ~ 2,
      `responsible research Practices_q14` == 'Rarely' ~ 3,
      `responsible research Practices_q14` == 'Occasionally' ~ 4,
      `responsible research Practices_q14` == 'Frequently' ~ 5,
      `responsible research Practices_q14` == 'Very Frequently' ~ 6,
      `responsible research Practices_q14` == 'Always' ~ 7
    ),
    rpq15 = case_when(
      `responsible research Practices_q15` == 'Never' ~ 7,
      `responsible research Practices_q15` == 'Very Rarely' ~ 6,
      `responsible research Practices_q15` == 'Rarely' ~ 5,
      `responsible research Practices_q15` == 'Occasionally' ~ 4,
      `responsible research Practices_q15` == 'Frequently' ~ 3,
      `responsible research Practices_q15` == 'Very Frequently' ~ 2,
      `responsible research Practices_q15` == 'Always' ~ 1
    ),
    rpq16 = case_when(
      `responsible research Practices_q16` == 'Never' ~ 1,
      `responsible research Practices_q16` == 'Very Rarely' ~ 2,
      `responsible research Practices_q16` == 'Rarely' ~ 3,
      `responsible research Practices_q16` == 'Occasionally' ~ 4,
      `responsible research Practices_q16` == 'Frequently' ~ 5,
      `responsible research Practices_q16` == 'Very Frequently' ~ 6,
      `responsible research Practices_q16` == 'Always' ~ 7
    ),
    rpq17 = case_when(
      `responsible research Practices_q17` == 'Never' ~ 1,
      `responsible research Practices_q17` == 'Very Rarely' ~ 2,
      `responsible research Practices_q17` == 'Rarely' ~ 3,
      `responsible research Practices_q17` == 'Occasionally' ~ 4,
      `responsible research Practices_q17` == 'Frequently' ~ 5,
      `responsible research Practices_q17` == 'Very Frequently' ~ 6,
      `responsible research Practices_q17` == 'Always' ~ 7
    ),
    rpq18 = case_when(
      `responsible research Practices_q18` == 'Never' ~ 7,
      `responsible research Practices_q18` == 'Very Rarely' ~ 6,
      `responsible research Practices_q18` == 'Rarely' ~ 5,
      `responsible research Practices_q18` == 'Occasionally' ~ 4,
      `responsible research Practices_q18` == 'Frequently' ~ 3,
      `responsible research Practices_q18` == 'Very Frequently' ~ 2,
      `responsible research Practices_q18` == 'Always' ~ 1
    ),
    rpq19 = case_when(
      `responsible research Practices_q19` == 'Never' ~ 7,
      `responsible research Practices_q19` == 'Very Rarely' ~ 6,
      `responsible research Practices_q19` == 'Rarely' ~ 5,
      `responsible research Practices_q19` == 'Occasionally' ~ 4,
      `responsible research Practices_q19` == 'Frequently' ~ 3,
      `responsible research Practices_q19` == 'Very Frequently' ~ 2,
      `responsible research Practices_q19` == 'Always' ~ 1
    ),
    rpq20 = case_when(
      `responsible research Practices_q20` == 'Never' ~ 1,
      `responsible research Practices_q20` == 'Very Rarely' ~ 2,
      `responsible research Practices_q20` == 'Rarely' ~ 3,
      `responsible research Practices_q20` == 'Occasionally' ~ 4,
      `responsible research Practices_q20` == 'Frequently' ~ 5,
      `responsible research Practices_q20` == 'Very Frequently' ~ 6,
      `responsible research Practices_q20` == 'Always' ~ 7
    )
  ) %>% # 1,2,10,12,13
  mutate(
    fpq1 = case_when(
      `fair research practices_q1` == 'Never' ~ 7,
      `fair research practices_q1` == 'Very Rarely' ~ 6,
      `fair research practices_q1` == 'Rarely' ~ 5,
      `fair research practices_q1` == 'Occasionally' ~ 4,
      `fair research practices_q1` == 'Frequently' ~ 3,
      `fair research practices_q1` == 'Very Frequently' ~ 2,
      `fair research practices_q1` == 'Always' ~ 1
    ),
    fpq2 = case_when(
      `fair research practices_q2` == 'Never' ~ 7,
      `fair research practices_q2` == 'Very Rarely' ~ 6,
      `fair research practices_q2` == 'Rarely' ~ 5,
      `fair research practices_q2` == 'Occasionally' ~ 4,
      `fair research practices_q2` == 'Frequently' ~ 3,
      `fair research practices_q2` == 'Very Frequently' ~ 2,
      `fair research practices_q2` == 'Always' ~ 1
    ),
    fpq3 = case_when(
      `fair research practices_q3` == 'Never' ~ 1,
      `fair research practices_q3` == 'Very Rarely' ~ 2,
      `fair research practices_q3` == 'Rarely' ~ 3,
      `fair research practices_q3` == 'Occasionally' ~ 4,
      `fair research practices_q3` == 'Frequently' ~ 5,
      `fair research practices_q3` == 'Very Frequently' ~ 6,
      `fair research practices_q3` == 'Always' ~ 7
    ),
    fpq4 = case_when(
      `fair research practices_q4` == 'Never' ~ 1,
      `fair research practices_q4` == 'Very Rarely' ~ 2,
      `fair research practices_q4` == 'Rarely' ~ 3,
      `fair research practices_q4` == 'Occasionally' ~ 4,
      `fair research practices_q4` == 'Frequently' ~ 5,
      `fair research practices_q4` == 'Very Frequently' ~ 6,
      `fair research practices_q4` == 'Always' ~ 7
    ),
    fpq5 = case_when(
      `fair research practices_q5` == 'Never' ~ 1,
      `fair research practices_q5` == 'Very Rarely' ~ 2,
      `fair research practices_q5` == 'Rarely' ~ 3,
      `fair research practices_q5` == 'Occasionally' ~ 4,
      `fair research practices_q5` == 'Frequently' ~ 5,
      `fair research practices_q5` == 'Very Frequently' ~ 6,
      `fair research practices_q5` == 'Always' ~ 7
    ),
    fpq6 = case_when(
      `fair research practices_q6` == 'Never' ~ 1,
      `fair research practices_q6` == 'Very Rarely' ~ 2,
      `fair research practices_q6` == 'Rarely' ~ 3,
      `fair research practices_q6` == 'Occasionally' ~ 4,
      `fair research practices_q6` == 'Frequently' ~ 5,
      `fair research practices_q6` == 'Very Frequently' ~ 6,
      `fair research practices_q6` == 'Always' ~ 7
    ),
    fpq7 = case_when(
      `fair research practices_q7` == 'Never' ~ 1,
      `fair research practices_q7` == 'Very Rarely' ~ 2,
      `fair research practices_q7` == 'Rarely' ~ 3,
      `fair research practices_q7` == 'Occasionally' ~ 4,
      `fair research practices_q7` == 'Frequently' ~ 5,
      `fair research practices_q7` == 'Very Frequently' ~ 6,
      `fair research practices_q7` == 'Always' ~ 7
    ),
    fpq8 = case_when(
      `fair research practices_q8` == 'Never' ~ 1,
      `fair research practices_q8` == 'Very Rarely' ~ 2,
      `fair research practices_q8` == 'Rarely' ~ 3,
      `fair research practices_q8` == 'Occasionally' ~ 4,
      `fair research practices_q8` == 'Frequently' ~ 5,
      `fair research practices_q8` == 'Very Frequently' ~ 6,
      `fair research practices_q8` == 'Always' ~ 7
    ),
    fpq9 = case_when(
      `fair research practices_q9` == 'Never' ~ 1,
      `fair research practices_q9` == 'Very Rarely' ~ 2,
      `fair research practices_q9` == 'Rarely' ~ 3,
      `fair research practices_q9` == 'Occasionally' ~ 4,
      `fair research practices_q9` == 'Frequently' ~ 5,
      `fair research practices_q9` == 'Very Frequently' ~ 6,
      `fair research practices_q9` == 'Always' ~ 7
    ),
    fpq10 = case_when(
      `fair research practices_q10` == 'Never' ~ 7,
      `fair research practices_q10` == 'Very Rarely' ~ 6,
      `fair research practices_q10` == 'Rarely' ~ 5,
      `fair research practices_q10` == 'Occasionally' ~ 4,
      `fair research practices_q10` == 'Frequently' ~ 3,
      `fair research practices_q10` == 'Very Frequently' ~ 2,
      `fair research practices_q10` == 'Always' ~ 1
    ),
    fpq11 = case_when(
      `fair research practices_q11` == 'Never' ~ 1,
      `fair research practices_q11` == 'Very Rarely' ~ 2,
      `fair research practices_q11` == 'Rarely' ~ 3,
      `fair research practices_q11` == 'Occasionally' ~ 4,
      `fair research practices_q11` == 'Frequently' ~ 5,
      `fair research practices_q11` == 'Very Frequently' ~ 6,
      `fair research practices_q11` == 'Always' ~ 7
    ),
    fpq12 = case_when(
      `fair research practices_q12` == 'Never' ~ 7,
      `fair research practices_q12` == 'Very Rarely' ~ 6,
      `fair research practices_q12` == 'Rarely' ~ 5,
      `fair research practices_q12` == 'Occasionally' ~ 4,
      `fair research practices_q12` == 'Frequently' ~ 3,
      `fair research practices_q12` == 'Very Frequently' ~ 2,
      `fair research practices_q12` == 'Always' ~ 1
    ),
    fpq13 = case_when(
      `fair research practices_q13` == 'Never' ~ 7,
      `fair research practices_q13` == 'Very Rarely' ~ 6,
      `fair research practices_q13` == 'Rarely' ~ 5,
      `fair research practices_q13` == 'Occasionally' ~ 4,
      `fair research practices_q13` == 'Frequently' ~ 3,
      `fair research practices_q13` == 'Very Frequently' ~ 2,
      `fair research practices_q13` == 'Always' ~ 1
    ),
    fpq14 = case_when(
      `fair research practices_q14` == 'Never' ~ 1,
      `fair research practices_q14` == 'Very Rarely' ~ 2,
      `fair research practices_q14` == 'Rarely' ~ 3,
      `fair research practices_q14` == 'Occasionally' ~ 4,
      `fair research practices_q14` == 'Frequently' ~ 5,
      `fair research practices_q14` == 'Very Frequently' ~ 6,
      `fair research practices_q14` == 'Always' ~ 7
    ),
    fpq15 = case_when(
      `fair research practices_q15` == 'Never' ~ 1,
      `fair research practices_q15` == 'Very Rarely' ~ 2,
      `fair research practices_q15` == 'Rarely' ~ 3,
      `fair research practices_q15` == 'Occasionally' ~ 4,
      `fair research practices_q15` == 'Frequently' ~ 5,
      `fair research practices_q15` == 'Very Frequently' ~ 6,
      `fair research practices_q15` == 'Always' ~ 7
    ),
    fpq16 = case_when(
      `fair research practices_q16` == 'Never' ~ 1,
      `fair research practices_q16` == 'Very Rarely' ~ 2,
      `fair research practices_q16` == 'Rarely' ~ 3,
      `fair research practices_q16` == 'Occasionally' ~ 4,
      `fair research practices_q16` == 'Frequently' ~ 5,
      `fair research practices_q16` == 'Very Frequently' ~ 6,
      `fair research practices_q16` == 'Always' ~ 7
    ),
    fpq17 = case_when(
      `fair research practices_q17` == 'Never' ~ 1,
      `fair research practices_q17` == 'Very Rarely' ~ 2,
      `fair research practices_q17` == 'Rarely' ~ 3,
      `fair research practices_q17` == 'Occasionally' ~ 4,
      `fair research practices_q17` == 'Frequently' ~ 5,
      `fair research practices_q17` == 'Very Frequently' ~ 6,
      `fair research practices_q17` == 'Always' ~ 7
    ),
    fpq18 = case_when(
      `fair research practices_q18` == 'Never' ~ 1,
      `fair research practices_q18` == 'Very Rarely' ~ 2,
      `fair research practices_q18` == 'Rarely' ~ 3,
      `fair research practices_q18` == 'Occasionally' ~ 4,
      `fair research practices_q18` == 'Frequently' ~ 5,
      `fair research practices_q18` == 'Very Frequently' ~ 6,
      `fair research practices_q18` == 'Always' ~ 7
    ),
    fpq19 = case_when(
      `fair research practices_q19` == 'Never' ~ 1,
      `fair research practices_q19` == 'Very Rarely' ~ 2,
      `fair research practices_q19` == 'Rarely' ~ 3,
      `fair research practices_q19` == 'Occasionally' ~ 4,
      `fair research practices_q19` == 'Frequently' ~ 5,
      `fair research practices_q19` == 'Very Frequently' ~ 6,
      `fair research practices_q19` == 'Always' ~ 7
    ),
    fpq20 = case_when(
      `fair research practices_q20` == 'Never' ~ 1,
      `fair research practices_q20` == 'Very Rarely' ~ 2,
      `fair research practices_q20` == 'Rarely' ~ 3,
      `fair research practices_q20` == 'Occasionally' ~ 4,
      `fair research practices_q20` == 'Frequently' ~ 5,
      `fair research practices_q20` == 'Very Frequently' ~ 6,
      `fair research practices_q20` == 'Always' ~ 7
    )
  ) %>%
  rowwise() %>%
  mutate(
    rpq = sum(c(rpq1, rpq2, rpq3, rpq4, rpq5, rpq6, rpq7, rpq8, rpq9, rpq10, rpq11, rpq12, rpq13, rpq14, rpq15, rpq16, rpq17, rpq18, rpq19, rpq20), na.rm = T),
    fpq = sum(c(fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20), na.rm = T)
  ) %>%
  mutate(`responsible research Practices score` = ifelse(rpq == 0, NA, rpq),
         `fair research practices score` = ifelse(fpq == 0, NA, fpq))
# g=final_dataset %>%
#   dplyr::select(`responsible research Practices_q1`, rpq1, `responsible research Practices_q2`, rpq2, `responsible research Practices_q8`, rpq8, `responsible research Practices_q14`, rpq14, `responsible research Practices_q18`, rpq18,
#                 `fair research practices_q1`, fpq1, `fair research practices_q5`, fpq5, `fair research practices_q9`, fpq9, `fair research practices_q10`, fpq10, `fair research practices_q12`, fpq12, `fair research practices_q14`, fpq14, `fair research practices_q17`, fpq17)
# x= final_dataset%>%
#   dplyr::select(rpq1, rpq2, rpq3, rpq4, rpq5, rpq6, rpq7, rpq8, rpq9, rpq10, rpq11, rpq12, rpq13, rpq14, rpq15, rpq16, rpq17, rpq18, rpq19, rpq20, fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20, `responsible research Practices score`, `fair research practices score`, rpq, fpq) #%>%
#   rowwise() %>%
# mutate(fp = sum(c(fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20), na.rm = T))

```


# Prevalence of responsible research practices and Fair research practices 

We used a cutoff score of 70 in both cases since the maximum score is 140 in both cases.
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
dt1 <- final_dataset %>%
  dplyr::select(rpq1, rpq2, rpq3, rpq4, rpq5, rpq6, rpq7, rpq8, rpq9, rpq10, rpq11, rpq12, rpq13, rpq14, rpq15, rpq16, rpq17, rpq18, rpq19, rpq20, fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20, `responsible research Practices score`, `fair research practices score`, `Which of the following best describes you?`) 
col_to_change <- c('rpq1', 'rpq2', 'rpq3', 'rpq4', 'rpq5', 'rpq6', 'rpq7', 'rpq8', 'rpq9', 'rpq10', 'rpq11', 'rpq12', 'rpq13', 'rpq14', 'rpq15', 'rpq16', 'rpq17', 'rpq18', 'rpq19', 'rpq20', 'fpq1', 'fpq2', 'fpq3', 'fpq4', 'fpq5', 'fpq6', 'fpq7', 'fpq8', 'fpq9', 'fpq10', 'fpq11', 'fpq12', 'fpq13', 'fpq14', 'fpq15', 'fpq16', 'fpq17', 'fpq18', 'fpq19', 'fpq20')
change_to <- c(1,2,3)
dt1[col_to_change] <- sapply(dt1[col_to_change],  # Replace values in certain columns
                              function(x) replace(x, x %in% change_to, 1))
change_to <- c(4,5,6,7,8)
dt1[col_to_change] <- sapply(dt1[col_to_change],  # Replace values in certain columns
                              function(x) replace(x, x %in% change_to, 0))
# change_to <- c(8)
# dt1[col_to_change] <- sapply(dt1[col_to_change],  # Replace values in certain columns
#                               function(x) replace(x, x %in% change_to, 2))
dt2 <-dt1 %>%
  mutate(
    rpq = sum(c(rpq1, rpq2, rpq3, rpq4, rpq5, rpq6, rpq7, rpq8, rpq9, rpq10, rpq11, rpq12, rpq13, rpq14, rpq15, rpq16, rpq17, rpq18, rpq19, rpq20), na.rm = T),
    fpq = sum(c(fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20), na.rm = T)
  ) %>%
  mutate(`responsible research Practices` = ifelse(rpq > 10, 'Fail', ifelse(rpq <= 10, 'Pass', 'NA')),
         `fair research practices` = ifelse(fpq > 10, 'Fail', ifelse(fpq <= 10, 'Pass', 'NA'))) %>%
  mutate(`responsible research Practices` = as.character(ifelse(is.na(`responsible research Practices score`), '', `responsible research Practices`)),
         `fair research practices` = as.character(ifelse(is.na(`fair research practices score`), '', `fair research practices`))
         ) %>%
  mutate(`responsible research Practices` = as.factor(ifelse(`responsible research Practices`=='', NA, `responsible research Practices`)),
         `fair research practices` = as.factor(ifelse(`fair research practices`=='', NA, `fair research practices`))) %>%
  dplyr::select(`responsible research Practices`, `fair research practices`, `Which of the following best describes you?`) %>%
  tbl_summary(by = `Which of the following best describes you?`#, 
            # missing = "no",
            # statistic = list(all_continuous() ~ "{mean} ({sd})")
            ) %>% 
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt2

# dt2 <- final_dataset %>%
#   mutate(location = as.factor(case_when(
#     `Which of the following best describes you?` == 'Researcher from the Global North' ~ 'Global North',
#     `Which of the following best describes you?` == 'Researcher from the Global South' ~ 'Global South'#,
#     # `Which of the following best describes you?` == '' ~ 'Global North',
#   ))) %>%
#   mutate(`responsible research Practices score` = as.factor(ifelse(`responsible research Practices score`>=70, 'Pass', ifelse(`responsible research Practices score`<70, 'Fail', 'NA'))),
#          `fair research practices score` = as.factor(ifelse(`fair research practices score`>=70, 'Pass', ifelse(`fair research practices score`<70, 'Fail', 'NA')))) %>%
#   dplyr::select(`responsible research Practices score`, `fair research practices score`, location) %>%
#   tbl_summary(by = location, 
#             missing = "no",
#             # statistic = list(all_continuous() ~ "{mean} ({sd})")
#             ) %>% 
#   add_p() %>%
#   add_n() %>% 
#   modify_header(label = "Variable") %>% # update the column header
#   bold_labels()
# dt2
```

# Demographics
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
dt01 <- final_dataset %>%
  dplyr::select(`Which country are you from?`, `What discipline of global health based describes you:`, `What is you gender?`, `How many years of involvement in research do you have?`, `Which of the following best describes you?`, `What is your highest academic rank?`) %>%
  # mutate(gender = factor(gender, labels = c('Females', 'Males'))) %>%
  tbl_summary(by = `Which of the following best describes you?`#, 
            # missing = "no",
            # statistic = list(all_continuous() ~ "{mean} ({sd})")
            ) %>% 
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

dt01
```


# Responsible research practices and fair research practices by the question which of the following best describes you?
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
dt02 <- final_dataset %>%
  dplyr::select(rpq1, rpq2, rpq3, rpq4, rpq5, rpq6, rpq7, rpq8, rpq9, rpq10, rpq11, rpq12, rpq13, rpq14, rpq15, rpq16, rpq17, rpq18, rpq19, rpq20, fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20, `responsible research Practices score`, `fair research practices score`, `Which of the following best describes you?`) %>%
  tbl_summary(by = `Which of the following best describes you?`, 
            # missing = "no",
            type = list(c('rpq1', 'rpq2', 'rpq3', 'rpq4', 'rpq5', 'rpq6', 'rpq7', 'rpq8', 'rpq9', 'rpq10', 'rpq11', 'rpq12', 'rpq13', 'rpq14', 'rpq15', 'rpq16', 'rpq17', 'rpq18', 'rpq19', 'rpq20', 'fpq1', 'fpq2', 'fpq3', 'fpq4', 'fpq5', 'fpq6', 'fpq7', 'fpq8', 'fpq9', 'fpq10', 'fpq11', 'fpq12', 'fpq13', 'fpq14', 'fpq15', 'fpq16', 'fpq17', 'fpq18', 'fpq19', 'fpq20', 'responsible research Practices score', 'fair research practices score') ~ 'continuous'),
            statistic = list(c('rpq1', 'rpq2', 'rpq3', 'rpq4', 'rpq5', 'rpq6', 'rpq7', 'rpq8', 'rpq9', 'rpq10', 'rpq11', 'rpq12', 'rpq13', 'rpq14', 'rpq15', 'rpq16', 'rpq17', 'rpq18', 'rpq19', 'rpq20', 'fpq1', 'fpq2', 'fpq3', 'fpq4', 'fpq5', 'fpq6', 'fpq7', 'fpq8', 'fpq9', 'fpq10', 'fpq11', 'fpq12', 'fpq13', 'fpq14', 'fpq15', 'fpq16', 'fpq17', 'fpq18', 'fpq19', 'fpq20', 'responsible research Practices score', 'fair research practices score') ~ "{median} ({p25}, {p75})")
            ) %>% 
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt02
```


# Responsible research practices and fair research practices by location (Global North or South)

In this analysis, I have removed those who chose the option prefer not to say
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
dt03 <- final_dataset %>%
  mutate(location = as.factor(case_when(
    `Which of the following best describes you?` == 'Researcher from the Global North' ~ 'Global North',
    `Which of the following best describes you?` == 'Researcher from the Global South' ~ 'Global South'#,
    # `Which of the following best describes you?` == '' ~ 'Global North',
  ))) %>%
  dplyr::select(rpq1, rpq2, rpq3, rpq4, rpq5, rpq6, rpq7, rpq8, rpq9, rpq10, rpq11, rpq12, rpq13, rpq14, rpq15, rpq16, rpq17, rpq18, rpq19, rpq20, fpq1, fpq2, fpq3, fpq4, fpq5, fpq6, fpq7, fpq8, fpq9, fpq10, fpq11, fpq12, fpq13, fpq14, fpq15, fpq16, fpq17, fpq18, fpq19, fpq20, `responsible research Practices score`, `fair research practices score`, location) %>%
  tbl_summary(by = location, 
            # missing = "no",
            type = list(c('rpq1', 'rpq2', 'rpq3', 'rpq4', 'rpq5', 'rpq6', 'rpq7', 'rpq8', 'rpq9', 'rpq10', 'rpq11', 'rpq12', 'rpq13', 'rpq14', 'rpq15', 'rpq16', 'rpq17', 'rpq18', 'rpq19', 'rpq20', 'fpq1', 'fpq2', 'fpq3', 'fpq4', 'fpq5', 'fpq6', 'fpq7', 'fpq8', 'fpq9', 'fpq10', 'fpq11', 'fpq12', 'fpq13', 'fpq14', 'fpq15', 'fpq16', 'fpq17', 'fpq18', 'fpq19', 'fpq20', 'responsible research Practices score', 'fair research practices score',) ~ 'continuous'),
            statistic = list(c('rpq1', 'rpq2', 'rpq3', 'rpq4', 'rpq5', 'rpq6', 'rpq7', 'rpq8', 'rpq9', 'rpq10', 'rpq11', 'rpq12', 'rpq13', 'rpq14', 'rpq15', 'rpq16', 'rpq17', 'rpq18', 'rpq19', 'rpq20', 'fpq1', 'fpq2', 'fpq3', 'fpq4', 'fpq5', 'fpq6', 'fpq7', 'fpq8', 'fpq9', 'fpq10', 'fpq11', 'fpq12', 'fpq13', 'fpq14', 'fpq15', 'fpq16', 'fpq17', 'fpq18', 'fpq19', 'fpq20', 'responsible research Practices score', 'fair research practices score') ~ "{median} ({p25}, {p75})")
            ) %>% 
  add_p(test = everything() ~ "wilcox.test") %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt03


```
# Multivariate model - responsible research Practices

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

dat <- final_dataset %>%
  mutate(Location = as.factor(case_when(
    `Which of the following best describes you?` == 'Researcher from the Global North' ~ 'Global North',
    `Which of the following best describes you?` == 'Researcher from the Global South' ~ 'Global South'#,
    # `Which of the following best describes you?` == '' ~ 'Global North',
  ))) %>%
  drop_na(c('Which country are you from?', 'What discipline of global health based describes you:', 'What is you gender?', 'How many years of involvement in research do you have?', 'Which of the following best describes you?', 'What is your highest academic rank?', 'responsible research Practices score', 'fair research practices score', 'Location')) %>%
  dplyr::select(`Which country are you from?`, `What discipline of global health based describes you:`, `What is you gender?`, `How many years of involvement in research do you have?`, Location, `What is your highest academic rank?`, `responsible research Practices score`, `fair research practices score`, ) 
univariate_table <- dat %>%
  mutate(rpq_score = `responsible research Practices score`) %>%
  mutate(
    accademic_rank = as.factor(`What is your highest academic rank?`),
    year_involment_research = as.factor(`How many years of involvement in research do you have?`),
    gender = as.factor(`What is you gender?`),
    country_origin = as.factor(`Which country are you from?`),
    discipline_global_health = as.factor(`What discipline of global health based describes you:`)
  ) %>%
  dplyr::select(rpq_score, Location, accademic_rank, year_involment_research, gender, country_origin, discipline_global_health) # %>%
univariate_table_1 <- 
tbl_uvregression(
  univariate_table[c("rpq_score", "Location", "accademic_rank", "year_involment_research", "gender", "country_origin", "discipline_global_health")],
  method = glm,
  y = "rpq_score",
  method.args = list(family = gaussian),
  exponentiate = FALSE
)
univariate_table_1
finalmodel_dataset <- dat %>%
  mutate(rpq_score = `responsible research Practices score`
         )%>%
  dplyr::select(rpq_score, Location, `What is your highest academic rank?`, `How many years of involvement in research do you have?`, `What is you gender?`, `Which country are you from?`, `What discipline of global health based describes you:`) %>%
  mutate(accademic_rank = as.factor(`What is your highest academic rank?`),
         year_involment_research = as.factor(`How many years of involvement in research do you have?`),
         gender = as.factor(`What is you gender?`),
         country_origin = as.factor(`Which country are you from?`),
         discipline_global_health = as.factor(`What discipline of global health based describes you:`)
         ) %>%
  dplyr::select(rpq_score, Location, accademic_rank, year_involment_research, gender, country_origin, discipline_global_health)

model <- glm(formula = as.formula('rpq_score~ Location + accademic_rank + year_involment_research + gender + country_origin + discipline_global_health'),
              data = finalmodel_dataset,
              family = gaussian,
              )

step.model <- stepAIC(model, direction = "both", 
                      trace = F)
# summary(step.model)
model1 <- glm(formula = as.formula('rpq_score~ Location + accademic_rank'),
              data = finalmodel_dataset,
              family = gaussian,
              )
m1 <-model1 %>%
  tbl_regression(
    estimate_fun = purrr::partial(style_ratio, digits = 2),# exponentiate = F, 
    pvalue_fun = ~style_pvalue(.x, digits = 3),
  ) %>% 
  # add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_gt() %>%
  gt::tab_source_note(gt::md("*Best set of dependent variables*")) %>%
  gt::gtsave(filename = "rrpq.pdf")
  # gt::gtsave(filename = "rrpq.rtf")

# full model
finalmodel_dataset2 <- dat %>%
  mutate(rpq_score = `responsible research Practices score`
         )%>%
  # dplyr::select(rpq_score, Location, var_selected) %>%
  mutate(accademic_rank = as.factor(`What is your highest academic rank?`),
         year_involment_research = as.factor(`How many years of involvement in research do you have?`),
         gender = as.factor(`What is you gender?`),
         country_origin = as.factor(`Which country are you from?`),
         discipline_global_health = as.factor(`What discipline of global health based describes you:`)
         ) %>%
  dplyr::select(rpq_score, Location, accademic_rank, year_involment_research, gender, country_origin, discipline_global_health)
model2 <- glm(formula = as.formula('rpq_score~ Location + accademic_rank + year_involment_research + gender + country_origin + discipline_global_health'),
              data = finalmodel_dataset2,
              family = gaussian,
              )

m2 <- model2 %>%
  tbl_regression(
    estimate_fun = purrr::partial(style_ratio, digits = 2),# exponentiate = F, 
    pvalue_fun = ~style_pvalue(.x, digits = 3),
  ) %>% 
  # add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_gt() %>%
  gt::tab_source_note(gt::md("*Full model*")) %>%
  gt::gtsave(filename = "rrpq - full model.pdf")
  # gt::gtsave(filename = "rrpq - full model.rtf")
```

# Multivariate model - Fair research Practices

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
dat <- final_dataset %>%
  mutate(Location = as.factor(case_when(
    `Which of the following best describes you?` == 'Researcher from the Global North' ~ 'Global North',
    `Which of the following best describes you?` == 'Researcher from the Global South' ~ 'Global South'#,
    # `Which of the following best describes you?` == '' ~ 'Global North',
  ))) %>%
  drop_na(c('Which country are you from?', 'What discipline of global health based describes you:', 'What is you gender?', 'How many years of involvement in research do you have?', 'Which of the following best describes you?', 'What is your highest academic rank?', 'responsible research Practices score', 'fair research practices score', 'Location')) %>%
  dplyr::select(`Which country are you from?`, `What discipline of global health based describes you:`, `What is you gender?`, `How many years of involvement in research do you have?`, Location, `What is your highest academic rank?`, `responsible research Practices score`, `fair research practices score`) 

univariate_table_2 <- dat %>%
  mutate(fpq_score = `fair research practices score`
         )%>%
  dplyr::select(fpq_score, Location, `What is your highest academic rank?`, `How many years of involvement in research do you have?`, `What is you gender?`, `Which country are you from?`, `What discipline of global health based describes you:`) %>%
  mutate(accademic_rank = as.factor(`What is your highest academic rank?`),
         year_involment_research = as.factor(`How many years of involvement in research do you have?`),
         gender = as.factor(`What is you gender?`),
         country_origin = as.factor(`Which country are you from?`),
         discipline_global_health = as.factor(`What discipline of global health based describes you:`)
         ) %>%
  dplyr::select(fpq_score, Location, accademic_rank, year_involment_research, gender, country_origin, discipline_global_health)
univariate_table_3 <- 
tbl_uvregression(
  univariate_table_2[c("fpq_score", "Location", "accademic_rank", "year_involment_research", "gender", "country_origin", "discipline_global_health")],
  method = glm,
  y = "fpq_score",
  method.args = list(family = gaussian),
  exponentiate = FALSE
)
univariate_table_3

finalmodel_dataset <- dat %>%
  mutate(fpq_score = `fair research practices score`
         )%>%
  dplyr::select(fpq_score, Location, `What is your highest academic rank?`, `How many years of involvement in research do you have?`, `What is you gender?`, `Which country are you from?`, `What discipline of global health based describes you:`) %>%
  mutate(accademic_rank = as.factor(`What is your highest academic rank?`),
         year_involment_research = as.factor(`How many years of involvement in research do you have?`),
         gender = as.factor(`What is you gender?`),
         country_origin = as.factor(`Which country are you from?`),
         discipline_global_health = as.factor(`What discipline of global health based describes you:`)
         ) %>%
  dplyr::select(fpq_score, Location, accademic_rank, year_involment_research, gender, country_origin, discipline_global_health)

model3 <- glm(formula = as.formula('fpq_score~ Location + accademic_rank + year_involment_research + gender + country_origin + discipline_global_health'),
              data = finalmodel_dataset,
              family = gaussian,
              )

step.model <- stepAIC(model3, direction = "both", 
                      trace = F)
summary(step.model)
model3 <- glm(formula = as.formula('fpq_score~ Location + year_involment_research'),
              data = finalmodel_dataset,
              family = gaussian,
              )

model3 %>%
  tbl_regression(
    estimate_fun = purrr::partial(style_ratio, digits = 2),# exponentiate = F, 
    pvalue_fun = ~style_pvalue(.x, digits = 3),
  ) %>% 
  # add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_gt() %>%
  gt::tab_source_note(gt::md("*Best set of dependent variables*"))%>%
  gt::gtsave(filename = "frpq.pdf")
  # gt::gtsave(filename = "frpq.rtf")

# full model
finalmodel_dataset3 <- dat %>%
  mutate(fpq_score = `fair research practices score`
         )%>%
  # dplyr::select(fpq_score, Location, var_selected) %>%
  mutate(accademic_rank = as.factor(`What is your highest academic rank?`),
         year_involment_research = as.factor(`How many years of involvement in research do you have?`),
         gender = as.factor(`What is you gender?`),
         country_origin = as.factor(`Which country are you from?`),
         discipline_global_health = as.factor(`What discipline of global health based describes you:`)
         ) %>%
  dplyr::select(fpq_score, Location, accademic_rank, year_involment_research, gender, country_origin, discipline_global_health)
model2 <- glm(formula = as.formula('fpq_score~ Location + accademic_rank + year_involment_research + gender + country_origin + discipline_global_health'),
              data = finalmodel_dataset3,
              family = gaussian,
              )

model2 %>%
  tbl_regression(
    estimate_fun = purrr::partial(style_ratio, digits = 2),# exponentiate = F, 
    pvalue_fun = ~style_pvalue(.x, digits = 3),
  ) %>% 
  # add_global_p() %>%
  bold_p(t = 0.05) %>%
  bold_labels() %>%
  italicize_levels() %>%
  as_gt() %>%
  gt::tab_source_note(gt::md("*Full model*"))%>%
  gt::gtsave(filename = "frpq-full_model.pdf")
  # gt::gtsave(filename = "frpq-full_model.rtf")
```

# Analysis for those who responded N/A
In this analysis, I have only tabulated those who said N/A in any of the 40 questions
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

dt1 <- final_dataset %>%
    dplyr::select(`responsible research Practices_q1`, `na_responsible research Practices_q1`, `Which of the following best describes you?`) %>%
    filter(`responsible research Practices_q1` == 'N/A') %>%
    dplyr::select(`na_responsible research Practices_q1`, `Which of the following best describes you?`) %>% #x[i], 
    tbl_summary(by = `Which of the following best describes you?`,
            # missing = "no",
            # statistic = list(all_continuous() ~ "{mean} ({sd})")
            ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt1

dt2 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q2`, `na_responsible research Practices_q2`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q2` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q2`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt2

dt3 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q3`, `na_responsible research Practices_q3`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q3` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q3`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt3

dt4 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q4`, `na_responsible research Practices_q4`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q4` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q4`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt4
dt5 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q5`, `na_responsible research Practices_q5`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q5` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q5`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt5
dt6 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q6`, `na_responsible research Practices_q6`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q6` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q6`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt6
dt7 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q7`, `na_responsible research Practices_q7`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q7` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q7`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt7
dt8 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q8`, `na_responsible research Practices_q8`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q8` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q8`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt8
dt9 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q9`, `na_responsible research Practices_q9`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q9` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q9`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt9
dt10 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q10`, `na_responsible research Practices_q10`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q10` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q10`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt10
dt11 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q11`, `na_responsible research Practices_q11`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q11` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q11`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt11
dt12 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q12`, `na_responsible research Practices_q12`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q12` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q12`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt12
dt13 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q13`, `na_responsible research Practices_q13`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q13` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q13`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt13
dt14 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q14`, `na_responsible research Practices_q14`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q14` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q14`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt14
dt15 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q15`, `na_responsible research Practices_q15`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q15` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q15`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt15
dt16 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q16`, `na_responsible research Practices_q16`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q16` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q16`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt16
dt17 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q17`, `na_responsible research Practices_q17`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q17` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q17`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt17
dt18 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q18`, `na_responsible research Practices_q18`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q18` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q18`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt18
dt19 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q19`, `na_responsible research Practices_q19`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q19` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q19`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt19
dt20 <- final_dataset %>%
  dplyr::select(`responsible research Practices_q20`, `na_responsible research Practices_q20`, `Which of the following best describes you?`) %>%
  filter(`responsible research Practices_q20` == 'N/A') %>%
  dplyr::select(`na_responsible research Practices_q20`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt20

```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
dt1 <- final_dataset %>%
  dplyr::select(`fair research practices_q1`, `na_fair research practices_q1`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q1` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q1`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt1

dt2 <- final_dataset %>%
  dplyr::select(`fair research practices_q2`, `na_fair research practices_q2`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q2` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q2`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt2

dt3 <- final_dataset %>%
  dplyr::select(`fair research practices_q3`, `na_fair research practices_q3`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q3` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q3`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt3

dt4 <- final_dataset %>%
  dplyr::select(`fair research practices_q4`, `na_fair research practices_q4`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q4` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q4`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt4
dt5 <- final_dataset %>%
  dplyr::select(`fair research practices_q5`, `na_fair research practices_q5`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q5` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q5`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt5
dt6 <- final_dataset %>%
  dplyr::select(`fair research practices_q6`, `na_fair research practices_q6`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q6` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q6`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt6
dt7 <- final_dataset %>%
  dplyr::select(`fair research practices_q7`, `na_fair research practices_q7`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q7` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q7`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt7
dt8 <- final_dataset %>%
  dplyr::select(`fair research practices_q8`, `na_fair research practices_q8`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q8` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q8`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt8
dt9 <- final_dataset %>%
  dplyr::select(`fair research practices_q9`, `na_fair research practices_q9`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q9` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q9`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt9
dt10 <- final_dataset %>%
  dplyr::select(`fair research practices_q10`, `na_fair research practices_q10`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q10` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q10`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt10
dt11 <- final_dataset %>%
  dplyr::select(`fair research practices_q11`, `na_fair research practices_q11`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q11` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q11`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt11
dt12 <- final_dataset %>%
  dplyr::select(`fair research practices_q12`, `na_fair research practices_q12`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q12` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q12`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt12
dt13 <- final_dataset %>%
  dplyr::select(`fair research practices_q13`, `na_fair research practices_q13`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q13` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q13`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt13
dt14 <- final_dataset %>%
  dplyr::select(`fair research practices_q14`, `na_fair research practices_q14`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q14` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q14`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt14
dt15 <- final_dataset %>%
  dplyr::select(`fair research practices_q15`, `na_fair research practices_q15`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q15` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q15`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt15
dt16 <- final_dataset %>%
  dplyr::select(`fair research practices_q16`, `na_fair research practices_q16`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q16` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q16`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt16
dt17 <- final_dataset %>%
  dplyr::select(`fair research practices_q17`, `na_fair research practices_q17`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q17` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q17`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt17
dt18 <- final_dataset %>%
  dplyr::select(`fair research practices_q18`, `na_fair research practices_q18`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q18` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q18`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt18
dt19 <- final_dataset %>%
  dplyr::select(`fair research practices_q19`, `na_fair research practices_q19`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q19` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q19`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt19
dt20 <- final_dataset %>%
  dplyr::select(`fair research practices_q20`, `na_fair research practices_q20`, `Which of the following best describes you?`) %>%
  filter(`fair research practices_q20` == 'N/A') %>%
  dplyr::select(`na_fair research practices_q20`, `Which of the following best describes you?`) %>% #x[i], 
  tbl_summary(by = `Which of the following best describes you?`,
    # missing = "no",
    # statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  # add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
dt20

```

