---
title: "Adddison's disease associated with advanced HIV may explain the high mortality"
author: "Dr Joseph B Sempa"
date: "`r Sys.Date()`"
output:
  word_document:
    fig_caption: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    toc: yes
  html_document:
    fig_caption: yes
    toc: yes
  html_notebook:
    toc: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(results = 'asis')
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(tinytex)
library(gmodels)
library(readxl)
# library(MASS)
library(gtsummary)
```


```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
final_dataset <- read_csv("final_dataset.csv", show_col_types = F) %>%
  mutate(outcome = ifelse(`Random cortisol result` < 500 & (`Synacthen: 30 minute cortisol result`< 550 & `ACTH result`> 13.9), 1, 0)) #%>%
# dat <- final_dataset %>%
# select(`Hospital folder number`,`Random cortisol result`, `ACTH sample drawn`, `ACTH result`, `Synacthen: 0 minute cortisol result`, `Synacthen: 30 minute cortisol result`, outcome)
# write.csv(dat, 'outcome_dat.csv')
```


```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
socio_demographics <- final_dataset %>%
  dplyr::select(`Age at enrolment`, Gender, Ethnicity)
tbl_summary(socio_demographics, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

# dt01 <- data.frame(`Primary medical conditions` = c(
#   final_dataset$`Primary medical conditions (1)`,
#   final_dataset$`Primary medical conditions (2)`,
#   final_dataset$`Primary medical conditions (3)`,
#   final_dataset$`Primary medical conditions (4)`,
#   final_dataset$`Primary medical conditions (5)`,
#   final_dataset$`Primary medical conditions (6)`,
#   final_dataset$`Primary medical conditions (7)`,
#   final_dataset$`Primary medical conditions (8)`,
#   final_dataset$`Primary medical conditions (9)`,
#   final_dataset$`Primary medical conditions (10)`
# )) #%>%
#   # dplyr::filter(!is.na(`Primary medical conditions`))
# 
# dt02 <- data.frame(`Co-existing medical conditions` = c(
#   final_dataset$`Co-existing medical conditions (1)`,
#   final_dataset$`Co-existing medical conditions (2)`,
#   final_dataset$`Co-existing medical conditions (3)`,
#   final_dataset$`Co-existing medical conditions (4)`,
#   final_dataset$`Co-existing medical conditions (5)`,
#   final_dataset$`Co-existing medical conditions (6)`,
#   final_dataset$`Co-existing medical conditions (7)`,
#   final_dataset$`Co-existing medical conditions (8)`,
#   final_dataset$`Co-existing medical conditions (9)`,
#   final_dataset$`Co-existing medical conditions (10)`
# )) #%>%
#   # filter(!is.na(`Co-existing medical conditions`))
# 
# dt03 <- data.frame(`Concomitant therapy` = c(
#   final_dataset$`Concomitant therapy (1)`,
#   final_dataset$`Concomitant therapy (2)`,
#   final_dataset$`Concomitant therapy (3)`,
#   final_dataset$`Concomitant therapy (4)`,
#   final_dataset$`Concomitant therapy (5)`,
#   final_dataset$`Concomitant therapy (6)`,
#   final_dataset$`Concomitant therapy (7)`,
#   final_dataset$`Concomitant therapy (8)`,
#   final_dataset$`Concomitant therapy (9)`,
#   final_dataset$`Concomitant therapy (10)`
# ))
# 
# dt04 <- cbind(dt01, dt02, dt03)
# tbl_summary(dt04, missing = "no") %>% 
#   modify_header(label = "Variable") %>% # update the column header
#   bold_labels()
  

clinical <- final_dataset %>%
  mutate(`days since employment` = as.Date(`Date of enrolment in study`)- as.Date(`Last Employment date`)) %>%
  dplyr::select(`HIV-positive, confirmed on ELISA`, `Total CD4 count...9`, `CD4 < 100`, `Opportunistic infection present`, `Oral or inhaled steroids in the last three months`, `days since employment`, `Duration of current illness`)
tbl_summary(clinical, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
opportunistic_infections <- final_dataset %>%
  dplyr::select(`Opportunistic infection  (choice=Tuberculosis)`, `Opportunistic infection  (choice=Cryptococcus neoformans)`, `Opportunistic infection  (choice=Toxoplasmosis)`, `Opportunistic infection  (choice=Mycobacterium avium-intracellulare)`, `Opportunistic infection  (choice=Kaposis sarcoma)`, `Opportunistic infection  (choice=Cytomegalovirus)`, `Opportunistic infection  (choice=Other)`) #, `Other, specify...67`
tbl_summary(opportunistic_infections, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table1 <- final_dataset %>%
  mutate(`log10 viral load` = log(`HIV viral load`, 10)) %>%
  dplyr::select(`BP (systolic)`, `BP (diastolic)`, `Heart rate`, Hypotension, Weakness, Tiredness, `Poor appetite`, `Weight loss`, `Increased pigmentation of the skin`, Nausea)
tbl_summary(signs_table1, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table2 <- final_dataset %>%
  mutate(`log10 viral load` = log(`HIV viral load`, 10)) %>%
  dplyr::select(Vomiting, `Liking for salt`, Hypoglycaemia, `Loss of consciousness`, Diarrhoea, Dizziness, Shock, Anorexia, `Loss of axillary and pubic hair, if female`, `Any postural drop in blood pressure`)
tbl_summary(signs_table2, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table3 <- final_dataset %>%
  mutate(`log10 viral load` = log(`HIV viral load`, 10)) %>%
  dplyr::select(`Presence of anaemia`, `Total CD4 count...89`, `log10 viral load`, `Or, HIV viral load = LDL (choice=LDL)`, `Current tuberculosis`, `Past tuberculosis`, `Electrolytes available`, Sodium, Potassium, Urea)
tbl_summary(signs_table3, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table4 <- final_dataset %>%
  mutate(`log10 viral load` = log(`HIV viral load`, 10)) %>%
  dplyr::select(Creatinine, `Full blood count (FBC) result available`, Haemoglobin, `White cell count`, Platelets, MCV, `Differential on FBC available`, Neutrophils, `Lymphocyte count`, Eosinophils, Basophils, `Aetiology of anaemia`) #, `Other, specify...112`
tbl_summary(signs_table4, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

outcome_variables <- final_dataset %>%
  mutate(`Random cortisol result coded` = cut(`Random cortisol result`, breaks = c(80,500,1400)),
         `ACTH result coded` = cut(`ACTH result`, breaks = c(0, 13.9, 500))
         ) %>%
  dplyr::select(`Random cortisol result`, `Random cortisol result coded`, `ACTH result`, `ACTH result coded`, `Antibodies sample drawn`, `Confirm random cortisol < 500 nmol/L`, `Confirm patient not on steroids for past 3 months`, `Synacthen: 0 minute cortisol result`, `Synacthen: 30 minute cortisol result`, outcome)
tbl_summary(outcome_variables, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

ctscan <- final_dataset %>%
  dplyr::select(`CT scan done`, `Bilateral adrenal enlargement`, `Calcification`, Atrophy, Haemorrhage, Nodularity, `Outcome of hospitalization`)
tbl_summary(ctscan, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

follow_up <- final_dataset %>%
  dplyr::select( `3 followup_done`, `3 followup_patientstatus`, `3 followup_patientcondition`, `6 followup_done`, `6 followup_patientstatus`, `6 followup_patientcondition`, `12 followup_done`, `12 followup_patientstatus`, `12 followup_patientcondition`, `If deceased, cause of death`)
tbl_summary(follow_up, missing = "no") %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
```

# comparison table: Outcome (hypoadrenalism status of study paticipants) vs other variables
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}
socio_demographics <- final_dataset %>%
  mutate(gender = as.factor(Gender),
         ethnicity = as.factor(Ethnicity)) %>%
  dplyr::select(`Age at enrolment`, gender, ethnicity, outcome) %>%
tbl_summary(by = outcome, missing = "no") %>% 
  add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
socio_demographics
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

# dt05 <- data.frame(`Primary medical conditions` = as.factor(c(
#   final_dataset$`Primary medical conditions (1)`,
#   final_dataset$`Primary medical conditions (2)`,
#   final_dataset$`Primary medical conditions (3)`,
#   final_dataset$`Primary medical conditions (4)`,
#   final_dataset$`Primary medical conditions (5)`,
#   final_dataset$`Primary medical conditions (6)`,
#   final_dataset$`Primary medical conditions (7)`,
#   final_dataset$`Primary medical conditions (8)`,
#   final_dataset$`Primary medical conditions (9)`,
#   final_dataset$`Primary medical conditions (10)`
# ))) %>%
#   mutate(id = rep(final_dataset$`Hospital folder number`, 10))
#   # dplyr::filter(!is.na(`Primary medical conditions`))
# 
# dt06 <- data.frame(`Co-existing medical conditions` = as.factor(c(
#   final_dataset$`Co-existing medical conditions (1)`,
#   final_dataset$`Co-existing medical conditions (2)`,
#   final_dataset$`Co-existing medical conditions (3)`,
#   final_dataset$`Co-existing medical conditions (4)`,
#   final_dataset$`Co-existing medical conditions (5)`,
#   final_dataset$`Co-existing medical conditions (6)`,
#   final_dataset$`Co-existing medical conditions (7)`,
#   final_dataset$`Co-existing medical conditions (8)`,
#   final_dataset$`Co-existing medical conditions (9)`,
#   final_dataset$`Co-existing medical conditions (10)`
# ))) %>%
#   mutate(id1 = rep(final_dataset$`Hospital folder number`, 10))
# 
# dt07 <- data.frame(`Concomitant therapy` = as.factor(c(
#   final_dataset$`Concomitant therapy (1)`,
#   final_dataset$`Concomitant therapy (2)`,
#   final_dataset$`Concomitant therapy (3)`,
#   final_dataset$`Concomitant therapy (4)`,
#   final_dataset$`Concomitant therapy (5)`,
#   final_dataset$`Concomitant therapy (6)`,
#   final_dataset$`Concomitant therapy (7)`,
#   final_dataset$`Concomitant therapy (8)`,
#   final_dataset$`Concomitant therapy (9)`,
#   final_dataset$`Concomitant therapy (10)`
# ))) %>%
#   mutate(id2 = rep(final_dataset$`Hospital folder number`, 10))
# 
# dt08 <- final_dataset %>%
#   mutate(id = final_dataset$`Hospital folder number`) %>%
#   dplyr::select(id, outcome) 
# 
# dt09 <- cbind(dt05, dt06, dt07) %>%
#   dplyr::select(id, `Primary.medical.conditions`, `Co.existing.medical.conditions`, `Concomitant.therapy`) %>%
#   left_join(dt08, by = c('id')) %>%
#   dplyr::select(`Primary.medical.conditions`, `Co.existing.medical.conditions`, `Concomitant.therapy`, outcome) %>%
# tbl_summary(#missing = "no", 
#             by = outcome,
#             label = list(`Primary.medical.conditions` ~ 'Primary medical conditions',
#                          `Co.existing.medical.conditions`~ 'Co existing medical conditions',
#                          `Concomitant.therapy` ~ 'Concomitant therapy'
#                          )
#             ) %>% 
#   add_p() %>%
#   add_n() %>%  
#   modify_header(label = "Variable") %>% # update the column header
#   bold_labels()
#  
# dt09 
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

clinical <- final_dataset %>%
  mutate(`days since employment` = as.Date(`Date of enrolment in study`)- as.Date(`Last Employment date`)) %>%
  mutate(`HIV-positive, confirmed on ELISA` = as.factor(`HIV-positive, confirmed on ELISA`),
         `Opportunistic infection present` = as.factor(`Opportunistic infection present`),
         `Oral or inhaled steroids in the last three months` = as.factor(`Oral or inhaled steroids in the last three months`)
         ) %>%
  dplyr::select(`HIV-positive, confirmed on ELISA`, `Total CD4 count...9`, `CD4 < 100`, `Opportunistic infection present`, `Oral or inhaled steroids in the last three months`, `days since employment`, `Duration of current illness`, outcome) %>%
tbl_summary(#clinical, 
            missing = "no",
            by = outcome,
            label = list(`Total CD4 count...9` ~ 'Total CD4 count')) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

clinical
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

# opportunistic_infections <- final_dataset %>%
#   mutate(
#     `Opportunistic infection  (choice=Tuberculosis)` = as.factor(`Opportunistic infection  (choice=Tuberculosis)`),
#     `Opportunistic infection  (choice=Cryptococcus neoformans)` = as.factor(`Opportunistic infection  (choice=Cryptococcus neoformans)`),
#     `Opportunistic infection  (choice=Toxoplasmosis)` = as.factor(`Opportunistic infection  (choice=Toxoplasmosis)`),
#     `Opportunistic infection  (choice=Mycobacterium avium-intracellulare)` = as.factor(`Opportunistic infection  (choice=Mycobacterium avium-intracellulare)`),
#     `Opportunistic infection  (choice=Kaposis sarcoma)` = as.factor(`Opportunistic infection  (choice=Kaposis sarcoma)`),
#     `Opportunistic infection  (choice=Cytomegalovirus)` = as.factor(`Opportunistic infection  (choice=Cytomegalovirus)`),
#     `Opportunistic infection  (choice=Other)` = as.factor(`Opportunistic infection  (choice=Other)`)
#   ) %>%
#   dplyr::select(`Opportunistic infection  (choice=Tuberculosis)`, `Opportunistic infection  (choice=Cryptococcus neoformans)`, `Opportunistic infection  (choice=Toxoplasmosis)`, `Opportunistic infection  (choice=Mycobacterium avium-intracellulare)`, `Opportunistic infection  (choice=Kaposis sarcoma)`, `Opportunistic infection  (choice=Cytomegalovirus)`, `Opportunistic infection  (choice=Other)`, outcome) %>% #, `Other, specify...67`
# tbl_summary(#opportunistic_infections,
#             missing = "no",
#             by = outcome,
#             label = list(`Opportunistic infection  (choice=Tuberculosis)` ~ 'Tuberculosis'),
#             `Opportunistic infection (choice=Cryptococcus neoformans)` ~ 'Cryptococcus neoformans',
#             `Opportunistic infection (choice=Toxoplasmosis)` ~ 'Toxoplasmosis',
#             `Opportunistic infection (choice=Mycobacterium avium-intracellulare` ~ 'Mycobacterium avium-intracellulare',
#             `Opportunistic infection (choice=Kaposis sarcoma)` ~ 'Kaposis sarcoma',
#             `Opportunistic infection (choice=Cytomegalovirus)` ~ 'Cytomegalovirus',
#             `Opportunistic infection (choice=Other)` ~ 'Other') %>% 
  # add_p() %>%
  # add_n() %>% 
#   modify_header(label = "Variable") %>% # update the column header
#   bold_labels()
# 
# opportunistic_infections
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

signs_table1 <- final_dataset %>%
  mutate(#`log10 viral load` = log(`HIV viral load`, 10),
         Hypotension = as.factor(Hypotension),
         Weakness = as.factor(Weakness),
         Tiredness = as.factor(Tiredness),
         `Poor appetite` = as.factor(`Poor appetite`),
         `Weight loss` = as.factor(`Weight loss`),
         `Increased pigmentation of the skin` = as.factor(`Increased pigmentation of the skin`),
         Nausea = as.factor(Nausea)
         ) %>%
  dplyr::select(`BP (systolic)`, `BP (diastolic)`, `Heart rate`, Hypotension, Weakness, Tiredness, `Poor appetite`, `Weight loss`, `Increased pigmentation of the skin`, Nausea, outcome) %>%
tbl_summary(#signs_table1, 
            missing = "no",
            by = outcome) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table1
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

signs_table2 <- final_dataset %>%
  mutate(
         Vomiting = as.factor(Vomiting),
         `Liking for salt` = as.factor(`Liking for salt`),
         Hypoglycaemia = as.factor(Hypoglycaemia),
         `Loss of consciousness` = as.factor(`Loss of consciousness`),
         Diarrhoea = as.factor(Diarrhoea),
         Dizziness = as.factor(Dizziness),
         Shock = as.factor(Shock),
         Anorexia = as.factor(Anorexia),
         `Loss of axillary and pubic hair, if female` = as.factor(`Loss of axillary and pubic hair, if female`),
         `Any postural drop in blood pressure` = as.factor(`Any postural drop in blood pressure`)
         ) %>%
  dplyr::select(Vomiting, `Liking for salt`, Hypoglycaemia, `Loss of consciousness`, Diarrhoea, Dizziness, Shock, Anorexia, `Loss of axillary and pubic hair, if female`, `Any postural drop in blood pressure`, outcome) %>%
tbl_summary(#signs_table2, 
            missing = "no",
            by = outcome) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table2
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

signs_table3 <- final_dataset %>%
  mutate(`log10 viral load` = log(`HIV viral load`, 10),
         `Presence of anaemia` = as.factor(`Presence of anaemia`),
         `Or, HIV viral load = LDL (choice=LDL)` = as.factor(`Or, HIV viral load = LDL (choice=LDL)`),
         `Current tuberculosis` = as.factor(`Current tuberculosis`),
         `Past tuberculosis` = as.factor(`Past tuberculosis`),
         `Electrolytes available` = as.factor(`Electrolytes available`)) %>%
  dplyr::select(`Presence of anaemia`, `Total CD4 count...89`, `log10 viral load`, `Or, HIV viral load = LDL (choice=LDL)`, `Current tuberculosis`, `Past tuberculosis`, `Electrolytes available`, Sodium, Potassium, Urea, outcome) %>%
tbl_summary(#signs_table3, 
            missing = "no",
            by = outcome,
            label = list(`Total CD4 count...89` ~ 'Total CD4 count'
                         )
            ) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table3
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

signs_table4 <- final_dataset %>%
  mutate(#`log10 viral load` = log(`HIV viral load`, 10),
    `Full blood count (FBC) result available` = as.factor(`Full blood count (FBC) result available`),
    `Differential on FBC available` = as.factor(`Differential on FBC available`),
    `Aetiology of anaemia` = as.factor(`Aetiology of anaemia`)
    ) %>%
  dplyr::select(Creatinine, `Full blood count (FBC) result available`, Haemoglobin, `White cell count`, Platelets, MCV, `Differential on FBC available`, Neutrophils, `Lymphocyte count`, Eosinophils, Basophils, `Aetiology of anaemia`, outcome) %>% #, `Other, specify...112`
tbl_summary(#signs_table4, 
            missing = "no",
            by = outcome) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

signs_table4
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

# outcome_variables <- final_dataset %>%
#   mutate(`Random cortisol result coded` = cut(`Random cortisol result`, breaks = c(80,500,1400)),
#          `ACTH result coded` = cut(`ACTH result`, breaks = c(0, 13.9, 500))
#          ) %>%
#   dplyr::select(`Random cortisol result`, `Random cortisol result coded`, `ACTH result`, `ACTH result coded`, `Antibodies sample drawn`, `Confirm random cortisol < 500 nmol/L`, `Confirm patient not on steroids for past 3 months`, `Synacthen: 0 minute cortisol result`, `Synacthen: 30 minute cortisol result`, outcome) %>%
# tbl_summary(outcome_variables, missing = "no") %>% 
#   modify_header(label = "Variable") %>% # update the column header
#   bold_labels()

ctscan <- final_dataset %>%
  mutate(`CT scan done` = as.factor(`CT scan done`),
         Nodularity = as.factor(Nodularity),
         `Bilateral adrenal enlargement` = as.factor(`Bilateral adrenal enlargement`),
         `Calcification` = as.factor(`Calcification`),
         Atrophy = as.factor(Atrophy),
         Haemorrhage = as.factor(Haemorrhage),
         `Outcome of hospitalization` = as.factor(`Outcome of hospitalization`)) %>%
  dplyr::select(`CT scan done`, `Bilateral adrenal enlargement`, `Calcification`, Atrophy, Haemorrhage, Nodularity, `Outcome of hospitalization`, outcome) %>%
tbl_summary(#ctscan, 
            missing = "no",
            by = outcome) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()

ctscan
```

```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

follow_up <- final_dataset %>%
  mutate(`3 followup_done` = as.factor(`3 followup_done`),
         `3 followup_patientstatus` = as.factor(`3 followup_patientstatus`),
         `3 followup_patientcondition` = as.factor(`3 followup_patientcondition`),
         `6 followup_done` = as.factor(`6 followup_done`),
         `6 followup_patientstatus` = as.factor(`6 followup_patientstatus`),
         `6 followup_patientcondition` = as.factor(`6 followup_patientcondition`),
         `12 followup_done` = as.factor(`12 followup_done`),
         `12 followup_patientstatus` = as.factor(`12 followup_patientstatus`),
         `12 followup_patientcondition` = as.factor(`12 followup_patientcondition`),
         `If deceased, cause of death` = as.factor(`If deceased, cause of death`)
         ) %>%
  dplyr::select( `3 followup_done`, `3 followup_patientstatus`, `3 followup_patientcondition`, `6 followup_done`, `6 followup_patientstatus`, `6 followup_patientcondition`, `12 followup_done`, `12 followup_patientstatus`, `12 followup_patientcondition`, `If deceased, cause of death`, outcome) %>%
tbl_summary(#follow_up, 
  missing = "no",
  by = outcome) %>% 
  add_p() %>%
  add_n() %>%  
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
follow_up
```

# Patients diagnosed with hypoadrenalism in advanced HIV study, compred to those with normal adreal function

patients with hypoadrenalism with advanced HIV (CD4<100) and not on steriods whether oral or injectable
```{r, message = FALSE, cache = TRUE, warning=FALSE, echo = FALSE, results='asis'}

socio_demographics <- final_dataset %>%
  mutate(outcome_advanced_HIV = ifelse(outcome==1 & `CD4 < 100`==1 & `Oral or inhaled steroids in the last three months`=='No', 1, 0)) %>%
  mutate(gender = as.factor(Gender),
         ethnicity = as.factor(Ethnicity)) %>%
  dplyr::select(`Age at enrolment`, gender, ethnicity, outcome_advanced_HIV) %>%
  tbl_uvregression(
    socio_demographics[c('outcome_advanced_HIV', 'Age at enrolment', 'gender', 'ethnicity')],
    method = glm,
    y = outcome_advanced_HIV,
    method.args = list(family = binomial),
    exponentiate = TRUE
  )
  
tbl_summary(by = outcome, missing = "no") %>% 
  add_p() %>%
  add_n() %>% 
  modify_header(label = "Variable") %>% # update the column header
  bold_labels()
socio_demographics

```